SST_patterns

### 2020-01-21 SST_patterns.Rmd
graphs

ggplot(data = Combined_frequency, aes(x = date, y = number_of_signals)) +
  geom_boxplot(aes(colour = product)) +
  theme(axis.text.x = element_text(angle = 90, hjust =1, vjust = 0.5))+
  #geom_smooth(aes(colour = product), method = "lm") +
  #labs(x = NULL) +
  facet_wrap(~site)

@@

>>>>

ggplot(data = Combined_frequency, aes(x = distance, y = number_of_signals)) +
  geom_boxplot(aes(colour = product)) +
  theme(axis.text.x = element_text(angle = 90, hjust =1, vjust = 0.5))+
  #geom_smooth(aes(colour = product), method = "lm") +
  #labs(x = NULL) +
  facet_wrap(~site)

ggplot(data = Combined_frequency, aes(x = date, y = number_of_signals, colour = product)) +
geom_point(aes(size = distance)) +
geom_smooth(method = "lm", size = 1.2)

ggplot(data = Combined_frequency, aes(x = date, y = number_of_signals, colour = product)) +
geom_bubble(aes(size = distance)) +
geom_smooth(method = "lm", size = 1.2)

@@

```{r}
library(hrbrthemes)
library(viridis)

ggplot(Combined_frequency, aes(x=t, y=number_of_signals, size=distance, color=product)) +
  geom_point(alpha=0.5) +
  facet_wrap(~site) +
  theme(axis.text.x = element_text(angle = 90, hjust =1, vjust = 0.5))

### Without time

ggplot(Combined_frequency, aes(x=distance, y= number_of_signals, color=product)) +
  geom_point(alpha=0.5) +
  facet_wrap(~site) +
  theme(axis.text.x = element_text(angle = 90, hjust =1, vjust = 0.5))
